Eclipse Che for Fair and Easy Education

### 2019-05-06 che.tex
Added Subsection for reproducible Research

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{he Plugin Arktik for Eclipse offered IoT Development with Che.While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of microservices \cite{IV18}, while being agile and reproducible.

\subsection{Faster Setup}
Onboarding new teammembers is made easy with Che. 
A newly joining member does not need to install IDEs, languages, tools and packages, he only needs access to his Che-Account and a singular workspace with every dependency build for him.
Depending on the complexitiy of the project this required atmost an hour. 
While this may seem long, the setup time is dependent on the complexity of the workspace. 
Setting up a complex workplace will also take more time manually. 
The work for this is done automatic and remote, so the user is free to dive into the documentation or have some coffee. 
His workspace will be able to launch the latest version immidieatly.
It is also notable, that the (technical) onboarding of developers and operators is streamlined into one single process.

@@

The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
Dependent on the setup, the attacker could also auto-deploy hidden spyware into a pro-
duction environment. 
While this is also a problem for normal developer teams, the fast pace of deployments with Che requires additional care. 
A rich CI/CD environment, such as a well-maintained Jenkins may lead to less-detailed code-reviews, as both unit- and end-to-end-tests succeed.  
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.

>>>>

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{he Plugin Arktik for Eclipse offered IoT Development with Che.While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of the several repositories provided from their university, and I expect most of these projects to be of scientific nature, 50\% of the research results where not reproducible.

The idea to not only ship code, but ship the experiment as a whole makes reproduction much easier. 
With Che (and using best practices for containers) the experiments done will be containerized and therefore reproducible. 
Even more complex environments including multiple components can be made in the same paradigms forming a pod. 
Such a pod could test applications working on an cassandra-cluster, fullstack web-applications or network-traffic-simulations.

Che also offers a whole new way of sharing the results: 
If a peer wants to inspect the code, he can be granted an account and get hands on the experiment without any setup. 
In an further attempt, a common guest-account can be established for anyone interested with read-only rights. 
This does not only help cooperation and understanding, but is also a good way to verify the results. 
At the moment we rather blindly trust each other about the results and data presented - we accepted that we are not able to reproduce it anyway or atleast not without inhuman effort. This changes with reproducible experiments, which verify the data and can help peers reviewing something even more important - the experiment itself. 
\subsection{Faster Setup}
Onboarding new teammembers is made easy with Che. 
A newly joining member does not need to install IDEs, languages, tools and packages, he only needs access to his Che-Account and a singular workspace with every dependency build for him.
Depending on the complexitiy of the project this required atmost an hour. 
While this may seem long, the setup time is dependent on the complexity of the workspace. 
Setting up a complex workplace will also take more time manually. 
The work for this is done automatic and remote, so the user is free to dive into the documentation or have some coffee. 
His workspace will be able to launch the latest version immidieatly.
It is also notable, that the (technical) onboarding of developers and operators is streamlined into one single process.

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
Dependent on the setup, the attacker could also auto-deploy hidden spyware into a pro-
duction environment. 
While this is also a problem for normal developer teams, the fast pace of deployments with Che requires additional care. 
A rich CI/CD environment, such as a well-maintained Jenkins may lead to less-detailed code-reviews, as both unit- and end-to-end-tests succeed.  
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.
